Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-07-29 Multiresolution_framework/ltx/manuscript.tex
shifted the frequency response of the wavelet to appendix

In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in Eqs.~(\eqref{eq:MRA-TwoScalepair1}-\eqref{eq:MRA-TwoScalepair2coefs}). 
In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
\subsection{Frequency Analysis}\label{sec:freq_anal}
To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline function needs to be computed by applying the Fourier transform to Eq.~\eqref{eq:N1convolutions}. To proceed the Fourier transform of $N_1(r)$ is first calculated, 
\begin{align}\label{eq:MRA-N1Fouriertransform}
\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu},
\end{align}
where $\nu$ is the spatial frequency and $i=\sqrt{-1}$. The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms. Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
\begin{align}\label{eq:MRA-NmFouriertransform}
\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^{m}.
\end{align}
The Fourier transform of the $m^{th}$ order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
\begin{align}      
	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2}  q_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{eq:MRA-Wavelettransform}
\end{align}
From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined. This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.
\section{State and Parameter Estimation}
The aim of this section is to describe the joint state-parameter estimation method used in this study, the expectation maximization (EM) algorithm. Here we provide a general description of the algorithm and also discuss the specific formulation for MRAIDE framework.

@@

>>>>

In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in Eqs.~(\eqref{eq:MRA-TwoScalepair1}-\eqref{eq:MRA-TwoScalepair2coefs}). 
In this paper, $4^{th}$ order cardinal B-spline scaling and wavelet functions are used, resulting in  $8^{th}$ and $12^{th}$ order B-spline functions when calculating Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Uij} respectively  whose values at integer points are given in Table~\ref{table:MRA-BsplineatIntegerPoints}.
\subsection{Frequency Analysis}\label{sec:freq_anal}
\parham{To determine the level of approximation in the model, $j$, detailed in the previous section, that is the number of basis functions required to reconstruct the field, $v_t(r)$, the frequency response of the B-spline wavelets is required and is given by (see~\ref{ap:FourierofBsplines}) 
\begin{align}      
	  \mathcal{F}(\varphi_{m}\left(r\right)) &=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu),\label{eq:MRA-Wavelettransform}
\end{align}
where $\nu$ is the spatial frequency and $i=\sqrt{-1}$. From Eq.~\eqref{eq:MRA-Wavelettransform} the frequency response of the wavelets and hence the level of approximation, $j$, can be determined. This way we choose wavelets up to level $j$ that can fully describe the spatial frequency contents of the underlying dynamics from the observed field.}
\section{State and Parameter Estimation}
The aim of this section is to describe the joint state-parameter estimation method used in this study, the expectation maximization (EM) algorithm. Here we provide a general description of the algorithm and also discuss the specific formulation for MRAIDE framework.

@@

\section{Fourier transform of B-spline wavelets}\label{ap:FourierofBsplines}
To calculate the frequency response of the B-spline wavelet the Fourier transform of $N_1(r)$ is first calculated, 
\begin{align}\label{eq:MRA-N1Fouriertransform}
\mathcal F(N_1(r))&=\int_{-\infty}^{+\infty}N_1(r)\mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
&=\int_{0}^{1} \mathrm{exp}(-2\pi i \nu r)dr \nonumber \\
&=\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu},
The convolution theorem states that the Fourier transform of the convolution of functions is equal to the product of their Fourier transforms. Therefore, taking Fourier transform of Eq.~\eqref{eq:N1convolutions} and substituting Eq.~\eqref{eq:MRA-N1Fouriertransform} for $\mathcal F(N_1(r)) $ yields
\begin{align}\label{eq:MRA-NmFouriertransform}
\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^{m}.
The Fourier transform of the $m^{th}$ order B-spline allows the calculation of the spatial frequency response of the wavelets using Eq.~\eqref{eq:MRA-TwoScalepair2} giving
	  \mathcal{F}(\varphi_{m}\left(r\right)) &= \sum_{n=0}^{3m-2}  q_n \mathcal{F}\left(N_{m}\left(2r-n\right)\right) \nonumber\\
	&=\frac{1}{2}\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m~\sum_{n=0}^{3m-2}  q_n \mathrm{exp}(-\pi in\nu).\label{app:MRA-Wavelettransform}
